---
title: "Data Sources"
description: |
  Thanks to Open Data Toronto!
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(opendatatoronto)
library(knitr)
library(tidyverse)
library(DT)
library(lubridate)
```

```{r data loading, echo = FALSE}
resources <- list_package_resources("8a6eceb2-821b-4961-a29d-758f3087732d")
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
data_source <- datastore_resources %>% 
  filter(row_number()==5) %>% 
  get_resource() %>% 
  select(OCCUPANCY_DATE, SHELTER_POSTAL_CODE, OCCUPANCY, CAPACITY) %>% 
  filter(CAPACITY > 0) %>% 
  mutate(SHELTER_POSTAL_CODE = str_sub(SHELTER_POSTAL_CODE, 1, 3)) %>% 
  mutate(PERCENT_OCCUPIED = OCCUPANCY/CAPACITY) %>% 
  mutate(OCCUPANCY_DATE = mdy(OCCUPANCY_DATE))
```

### Credits

The data for this project was sourced from [Open Data Toronto](https://www.toronto.ca/city-government/data-research-maps/open-data/).

* To replicate my project, install the Open Data Toronto R package `(install.packages("opendatatoronto"))`.
* The specific package I used was *8a6eceb2-821b-4961-a29d-758f3087732d*, row 5 of this package resource.
* You can find detailed documentation of the Daily Shelter Occupancy Dataset here: [Daily Shelter Occupancy](https://open.toronto.ca/dataset/daily-shelter-occupancy/)

### Data as a Table
If you don't care to download the raw data and explore it by yourself, you can find the raw data in the table below here. Happy scrolling!

```{r table}
datatable(data_source)
```


