---
title: "Toronto Shelter Data in 2020"
description: |
  This project visualizes the percentage occupation of Toronto Shelters in the year 2020.
bibliography: bibliography.bib
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(opendatatoronto)
library(distill)

```

```{r getting the rds for overview, echo = FALSE}
overview_plot <- read_rds("overview.rds")
```

```{r displaying the plot}
overview_plot
```

## Broad Trends
It's clear that winter months tend to have the highest occupancy ratios, with the average occupancy rate on January 24th, 2020 being **97%**. This could most likely be attributed to the lower temperatures, with the average temperature in January and February being around -5째C (23째F), but with the lows dipping down to -16째C (3.2째F). However, it is also clear that COVID-19 had a significant impact on occupancy rates, as shelters, even during December 2020, did not regain their occupancy rates and stayed at around 77%, possibly due to requirements put in by the City to limit the spread of the disease. Check out [Postal Codes](postal-code.html) to see trends in your area. [@weather]

*N.B.*: the plot is interactive! Click on it and hover your cursor above the line to view occupancy rates from individual dates.